Title

### 2014-07-23 paper.tex
more on the result

@@

After the 320 sample comments have been labeled,
they are scored based on the number of ``yes'' given to the sample.
The table below shows the distribution of scores for the training data.

\begin{center}
\begin{tabular}{|r|r|}
\hline
\bfseries Score & \bfseries Count \\
\hline
0 & 87 \\ 1 & 60 \\ 2 & 51 \\ 3 & 122 \\
\hline
\end{tabular}
\end{center}

@@

From our training data,
the following criteria have been found:

For ``yes'' result:
\begin{gather*} similarity \geq 0.015528969196702956 \text{ and}\\ distance \leq 2.4949438168165483 \end{gather*}

For ``no'' result:
\begin{gather*} similarity \leq 0.08752176628812282 \text{ and}\\ distance \geq 2.26567908457803 \end{gather*}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=3in]{vector}
\caption{The similarity and distance metric that is being used.}
\label{fig:vector}
\end{figure}

@@

After the 320 sample comments have been labeled,
they are scored based on the number of ``yes'' given to the sample.
There were 87, 60, 51, and 122 comments with scores of 0, 1, 2, and 3, respectively.

@@

% the criteria that were found
From our training data,
the following criteria have been obtained that maximizes the F$_1$ score:

Criteria to find samples with score of 3 (``positive''):
\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
\\ \text{(F$_1$-score: 0.741313)} \end{gather*}

Criteria to find samples with score of 0 (``negative''):
\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
\\ \text{(F$_1$-score: 0.725389)}\end{gather*}

Note that these constant values can vary from project to project, and thus is not a universal constant.

% run result

Running our model against the training data gives us the result displayed in the following table.
In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.

\begin{center}
\begin{tabular}{|r|rrrr|}
\hline
& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
\hline
Negative & 69 & 23 & 7 & 6 \\
Neither & 12 & 24 & 20 & 20 \\
Overlap & 1 & 1 & 0 & 1 \\
Positive & 4 & 13 & 24 & 95 \\
\hline
\end{tabular}
\end{center}

As expected, most comments classified as \emph{negative} have score of 0 and 1,
while most \emph{positive} comments have score of 2 and 3.
However, some comments in every score were lost and classified as \emph{neither}.

% cross validation result
